Manuscript figures

### 2024-04-29 manuscript_plots.Rmd
add package install

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(arrow)
library(lubridate)
library(tidytext)
library(ggpattern)
library(ggpubr)
library(ggh4x)
```
## Get scores

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(arrow)
library(lubridate)
library(tidytext)
library(ggpattern)
library(ggpubr)
library(ggh4x)
source('install_packages.R')
```
## Get scores
